You are the way you structurally talk: Structural-temporal neighborhoods of posts to characterize users in online forums

### 2016-03-29 doc/paper.tex
minor

\subsection{Structural neighborhoods in discussion trees}

@@

\subsection{Structuro-temporal neighborhoods in discussion trees}
\begin{definition}
Given a tree graph $G$, the \textit{structural-temporal neighborhood} of distance $d$ of post $i$, denoted as $\mathcal{N}_{i}^T(r,n)$ is the induced subgraph from its structural neighborhood composed the $n$ vertices that are closer to $i$ in time and for which there exists a path to $i$ in $\mathcal{N}_{i}^T(r,n)$.  
\end{definition}

@@

Note that this definition does not consider the timestamp of posts but only the order in which they arrived. An alternative definition of structural-temporal neighborhood might include not the $o$  posts that are closest to the ego post, but every post $j$ at distance $|t_i-t_j|<\tau$ from the ego post $i$. However, both options consider that the local dynamic ends at a fixed horizon ($o$ or $\tau$). This is specially problematic for the case of $\tau$ since different conversation threads may grow at different speeds, as well as different parts of the same thread or even the same part of the thread at different moments (e.g. threads barely grow at night). If we were to use $\tau$ as temporal horizon, we need a mechanism to automatically decide the proper $\tau$ for every post.

\begin{definition}
Let $s={p^{(1)},...p^{(m)}}$ be the sequence of posts in the structural neighbourhood $\mathcal{N}_i(r)$ ordered by their temporal distance to $i$. Let $\pi=\{\Delta t_1,...,\Delta t_M\}$ be the sequence of time differences between a post in $s$ and its predecessor in $s$. The \textit{temporal radius} $\tau$ of the neighbourhood is the timestamp of the last post $k$ whose $\Delta t_k$ comes from the same distribution than its predecessors $\Delta t_{k-1},..., \Delta t_{1}$ (an intuition for this definition is given in Figure~\ref{fig:cutpoints})
\end{definition}

According to the above definition, to find the temporal radius we need to find the first outlier in a sequence of $\Delta t$. Assuming the $\Delta t_i$ comes from an Exponential distribution, and that its $\lambda$ parameter comes itself from a Gamma distribution, we can exploit this conjugacy and obtain the analytical form of the probability of a given $\Delta t_k$ of belonging to the same distribution than its predecessors:
\begin{equation}
p(\Delta t_k | \Delta t_1,...\Delta t_{k-1})
=
\int p(\Delta t_k | \lambda_{k-1})p(\lambda_{k-1} |\Delta t_1,...\Delta t_{k-1})
=\frac{(\beta + n\overline{x})^{\alpha+n}}{(\beta + n\overline{x}+\Delta t_k)^{\alpha+n+1}}(\alpha+n)
\end{equation}
Details of this derivation are given in the Appendix.

>>>>

@@

\section{Structuro-temporal neighborhoods in discussion trees}
\subsection{Order-based}
\begin{definition}
Given a tree graph $G$, the \textit{structural-temporal neighborhood} of distance $d$ of post $i$, denoted as $\mathcal{N}_{i}^T(r,n)$ is the induced subgraph from its structural neighborhood composed the $n$ vertices that are closer to $i$ in time and for which there exists a path to $i$ in $\mathcal{N}_{i}^T(r,n)$.  
\end{definition}

@@

\subsection{Time-based}
Note that this definition does not consider the timestamp of posts but only the order in which they arrived. An alternative definition of structural-temporal neighborhood might include not the $o$  posts that are closest to the ego post, but every post $j$ at distance $|t_i-t_j|<\tau$ from the ego post $i$. However, both options consider that the local dynamic ends at a fixed horizon ($o$ or $\tau$). This is specially problematic for the case of $\tau$ since different conversation threads may grow at different speeds, as well as different parts of the same thread or even the same part of the thread at different moments (e.g. threads barely grow at night). If we were to use $\tau$ as temporal horizon, we need a mechanism to automatically decide the proper $\tau$ for every post.

\begin{definition}
Given the set of posts from the root to any leaf, a post $p_i$ is a \textit{vertical breakpoint} if the time between $p_i$ and its parent is at least twice the median of the time lapses in the chain  $\Delta$ is   $\Delta_i < 2 \Delta_{median}$
\end{definition}

\begin{definition}
Given the set of posts from the root to any leaf, a post is a \textit{horizontal breakpoint} if its $\Delta$ is   $\frac{\Delta_i}{\Delta_{median}}>2$
\end{definition}

\begin{definition}
Let $s={p^{(1)},...p^{(m)}}$ be the sequence of posts in the structural neighbourhood $\mathcal{N}_i(r)$ ordered by their temporal distance to $i$. The temporal neighborhood is the subgraph that belongs to the same dynamic than the ego post 
(an intuition for this definition is given in Figure~\ref{fig:cutpoints})
\end{definition}

According to the above definition, to find the temporal radius we need to find the first outlier in a sequence of $\Delta t$. Assuming the $\Delta t_i$ comes from an Exponential distribution, and that its $\lambda$ parameter comes itself from a Gamma distribution, we can exploit this conjugacy and obtain the analytical form of the probability of a given $\Delta t_k$ of belonging to the same distribution than its predecessors.
